Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-18 analysis/paper/paper.Rmd
remove duplicate data files and edit path

```
```{r}

@@

lands <- readland.tps(
  here::here("data/derived_data/landmarks.tps"),
  specID = "ID")

@@

```
<!-- QH: Later on, the language "the visualization above" will be changed to "Figure X." -->
<!-- QH: Also, on a secondary note, I had to copy the data file into a different location. That means that there are redundant data files that will need to be cleaned up later -->

>>>>

```{r}

@@

lands <- readland.tps(
  here::here("analysis/data/derived_data/landmarks.tps"),
  specID = "ID")

@@

<!-- QH: Later on, the language "the visualization above" will be changed to "Figure X." -->
<!-- QH: Also, on a secondary note, I had to copy the data file into a different location. That means that there are redundant data files that will need to be cleaned up later -->
